---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# loftgaedi

<!-- badges: start -->
<!-- badges: end -->

The purpose of this package is to make air quality data from [loftgaedi.is](https://loftgaedi.is) easily accessible to R users. It does this by providing helper functions -`get_latest()`, `get_dates()` and `get_stations()`- that interface with the API and transform the content to tidy tables. In addition to these, datasets containing all measurements from 2015-01-01 to 2022-12-31 is incudluded as `loftgaedi_2015` up to `loftgaedi_2022`.

## Installation

You can install the development version of loftgaedi like so:

``` r
remotes::install("bgautijonsson/loftgaedi")
```

## Examples

```{r example}
library(loftgaedi)
```

### `get_latest()`

This function provides all air quality data that was recorded in the last 24 hours, updated hourly at approximately 17 minutes past.

```{r}
d <- get_latest()

dplyr::glimpse(d)
```



### `get_dates(dates)`

This function fetches data from the provided dates. The `dates` input must be a vector of dates or coercible to date format.

```{r}
my_dates <- seq.Date(from = as.Date("2023-01-01"), to = as.Date("2023-01-11"), by = "days")
d <- get_dates(my_dates)

dplyr::glimpse(d)
```

### `get_stations()`

This function provides basic information about all stations *(location, activity window, altitude etc.)* in the data.

```{r}
d <- get_stations()

dplyr::glimpse(d)
```


### `loftgaedi_data`


```{r}
dplyr::glimpse(loftgaedi_2015)
```

